Functional oxide layers for electrical isolation and chemical passivation of steel substrates

### 2022-05-22 Thesis/chapter/03-theoretical-background.tex
IR fast

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{Infrared Absorption and Spectroscopy}
\td{IR around page 45;
REFLECTIVITY? can also be used for determination of thickness p47
}
\td{what, how, why?}
\td{QUESTIONS: 
	how does a IR spectr work? monochromator or FT 
	how does FT work 
	how does a beam splitter work? 
	how does detector work? two different for UVVis and MIR
}

%%% WHAT? 
\Gls{ir} spectroscopy is a molecular spectroscopic method using interactions of \gls{ir} light (wavelengths $\lambda$ of between \num{e-3} and \num{e-6}\m{}
or wave numbers of 500 to \pcm{4000} ) with molecules. \cite{Schwedt2008}
In general, light is described as periodic \gls{em} wave 
which - in vacuum - moves with the speed of light ($c = \mps{299792458}$).
The relation of energy~$E$ of a photon, its frequency~$\nu$, wavelength~$\lambda$ and wave number~$\bar{\nu}$ are as follows:
\begin{align*}
	E &= h \cdot \nu \\
	\nu &= c/ \lambda \\
	\bar{\nu} &= 1/\lambda,
\end{align*}
where $h$ is the Planck's constant.
%In words: shorter wavelength (higher frequency) photons are more energetic.
In practice the spectrum of \gls{em} waves is sectioned into different ranges (\td{see figure?});
from high to low energy: X-ray, \gls{uv}, \gls{vis}, (near, middle and far) \gls{ir}, microwaves and radio waves. 
\td{with number?}
X-rays interact with core electrons, \gls{uv}\gls{vis} with valence electrons, \gls{ir} with molecular vibrations, microwaves with molecular rotations and radio with electron and nuclear spins. 
%Molecular vibrations can be separated in valence and deformation vibrations.
%
A molecule has $F=3N$ ($N$ number of atoms) degrees of freedom, including translational $F_T=3$ and rotational $F_R=3$ (2 for linear molecules) movements. 
%
The number of vibrations can therefore calculated as 
\begin{align*}
	F_V &= 3N - F_T - F_R = 3N - 6 \\
	F_V &= 3N - F_T - F_R = 3N - 5 \textrm{ (for linear molecules)}.
\end{align*}
%wodurch sich die anzahl der vibration reduces to $F_V=3N-6$ ($3N-5$) for vibrations. 
Vibrations are classified in valence vibrations (change of bond length) and deformation (change of bindungs angle) vibrations\cite{Melker2006}. 
Only vibrations that change the dipole moment of the molecule are \gls{ir} active.

%\td{describe simple IR with monochromator}
%\paragraph{\Gls{IR} Spectrometer}

\paragraph{(Fourier Transform) Infrared spectrometer}
 A ceramic material (Nernst glower) is heated to \oc{1600} as light source. 
 In the two beam spectrometer the light is split, send through the sample and a reference and alternately send through a monochromator to a detector (thermocouple). 
In the \gls{ft}\gls{ir} spectrometer the beam is send through the sample, split and reflected from a static and from a moving mirror, recombined and detected by a photo multiplier (a device which transforms photons into electrical signals). 
\td{In a \gls{ft}\gls{ir} spectrometer the reference has to be measured before the sample, individually}

\td{FREE WRITING:}
Absorbance per din 1349: $A(\lambda) = \log{\frac{\phi_{in}}{\phi_{ex}}}$ and transmission $\tau =T=D= \phi_{ex}/\phi_{in}$
The absorbance intensity is dependent on wave length and molecule structure. 
%\td{Frank-Condon rules, spin verbot and symmetrie verbot are ausschlaggebend für the resulting spectrum. }
%differences to \gls{uv}\gls{vis}: transmission instead of absorbance, higher energy left instead right in plot, base line on top instead of bottom.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{X-Ray Diffraction}
%\url{https://link.springer.com/content/pdf/10.1186/2228-5326-3-8.pdf}
\gls{xrd} is used to study the crystalline strucutre of materlias since X-rays wavelengths (between 0.2 and \nm{10}) are comparable to the interatomic spacing of crystalline solids.  \cite{Kaliva2020}.
Each crystalline material has discreet atomc structure, which upon irradiation with X-rays causes constructive and destructive interference and generates unique diffraction patterns. 
XRD \td{spectra} of crystalline materials feature distinct peaks, whereas amorphous materials exhibit a broad cruve with a maximum extending over several degrees (2$\theta$).

\url{https://chem.libretexts.org/Courses/Franklin_and_Marshall_College/Introduction_to_Materials_Characterization__CHM_412_Collaborative_Text/Diffraction_Techniques/X-ray_diffraction_(XRD)_basics_and_application}\\

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{Infrared Absorption and Spectroscopy}
\td{IR around page 45;
REFLECTIVITY? can also be used for determination of thickness p47\cite{Dumin1967}
}
\td{QUESTIONS: 
	how does a beam splitter work? 
	how does detector work? two different for UVVis and MIR
}

%%% WHAT? 
\Gls{ir} spectroscopy is a molecular spectroscopic method using interactions of \gls{ir} light (wavelengths $\lambda$ of \num{e-3} to \num{e-6}\m{}
or wave numbers $\bar{\nu}$ of 500 to \pcm{4000} ) with molecules. \cite{Schwedt2008}
In general, light is described as periodic \gls{em} wave 
which - in vacuum - moves with the speed of light ($c = \mps{299792458}$).
The relation of energy~$E$ of a photon, its frequency~$\nu$, wavelength~$\lambda$ and wave number~$\bar{\nu}$ are as follows:
\begin{align*}
	E &= h \cdot \nu \\
	\nu &= c/ \lambda \\
	\bar{\nu} &= 1/\lambda,
\end{align*}
where $h$ is the Planck's constant.
%In words: shorter wavelength (higher frequency) photons are more energetic.
In practice the spectrum of \gls{em} waves is sectioned into different ranges (\td{see figure?});
from high to low energy: X-ray, \gls{uv}, \gls{vis}, (near, middle and far) \gls{ir}, microwaves and radio waves. 
\td{with number?}
X-rays interact with core electrons, \gls{uv}\gls{vis} with valence electrons, \gls{ir} with molecular vibrations, microwaves with molecular rotations and radio with electron and nuclear spins. 
%Molecular vibrations can be separated in valence and deformation vibrations.
%
A molecule has $F=3N$ ($N$ number of atoms) degrees of freedom, including translational $F_T=3$ and rotational $F_R=3$ (2 for linear molecules) movements. 
%
The number of vibrations can therefore calculated as 
\begin{align*}
	F_V &= 3N - F_T - F_R = 3N - 6 \\
	F_V &= 3N - F_T - F_R = 3N - 5 \textrm{ (for linear molecules)}.
\end{align*}
Vibrations are classified in valence vibrations (change of bond length) and deformation (change of bond angle) vibrations\cite{Melker2006}. 
Only vibrations that change the dipole moment of the molecule are \gls{ir} active.

%\td{describe simple IR with monochromator}

\paragraph{(Fourier Transform) Infrared spectrometer}
 A ceramic material (Nernst glower) is heated to around \oc{1600} as light source. 
 In the two-beam-spectrometer the light is split, sent through the sample and a reference and alternately sent through a monochromator to a detector (thermocouple). 
%
In the \gls{ft}\gls{ir} spectrometer the beam is sent through the sample, split and 
reflected from a static and from a moving mirror, recombined and detected by a photo 
multiplier (a device which transforms photons into electrical signals). 
How the two beams will interfere upon recombination depends on the optical path difference (also called retardation) of the two light beams.
\td{In a \gls{ft}\gls{ir} spectrometer the reference has to be measured before the sample, individually}

\td{FREE WRITING:}
Absorbance per din 1349: $A(\lambda) = \log{\frac{\phi_{in}}{\phi_{ex}}}$ and transmission $\tau =T=D= \phi_{ex}/\phi_{in}$
The absorbance intensity is dependent on wave length and molecule structure. 
%\td{Frank-Condon rules, spin verbot and symmetrie verbot are ausschlaggebend für the resulting spectrum. }
%differences to \gls{uv}\gls{vis}: transmission instead of absorbance, higher energy left instead right in plot, base line on top instead of bottom.
When the refractive index of two layers differ, \gls{ir} can be used to measure the thickness\cite{Dumin1967}.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{X-Ray Diffraction}
%\url{https://link.springer.com/content/pdf/10.1186/2228-5326-3-8.pdf}
\gls{xrd} is used to study the crystalline structure of materials.
Since X-rays wavelengths (\num{0.2} to \nm{10}) are comparable to the interatomic spacing of crystalline solids the beams get reflected and contain information about the structure\cite{Kaliva2020}.
Each crystalline material has a discreet atomic structure, which upon irradiation with 
X-rays causes constructive and destructive interference according to Bragg's law and generates unique diffraction patterns. 
\Gls{xrd} diffraction plots of crystalline materials feature distinct peaks, whereas amorphous materials exhibit a broad curve with a maximum extending over several degrees (2$\theta$).

%\url{https://chem.libretexts.org/Courses/Franklin_and_Marshall_College/Introduction_to_Materials_Characterization__CHM_412_Collaborative_Text/Diffraction_Techniques/X-ray_diffraction_(XRD)_basics_and_application}\\
